02_DESeq_characterization

### 2019-07-24 analysis/03_DESeq2_characterization.Rmd
now with options

>>>>

musicgenes5 <- function(mygroup, mysusbtitle){
  myplot <- candidataCountsTcol2 %>%
  filter(sextissue %in% c(mygroup),
         gene == "GAL") %>%
    ggplot(aes(x = treatment, y = mean)) +
    geom_point(colour = "white") + 
    theme_minimal() +
    facet_wrap(~gene,  ncol = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "italic"),
          panel.grid = element_blank()) +
    geom_image(aes(image="https://storage.needpix.com/rsynced_images/music-34177_1280.png")) +
   labs(y = "mean gene expression", subtitle = mysusbtitle, x = NULL) +
    ylim(c(20,70))

a <- musicgenes5("female_hypothalamus", "female hypothalamus")
b <- musicgenes5("male_hypothalamus", "male hypothalamus")

pdf("../figures/characterization/musicalgenes-6.pdf", width = 6, height = 3)
plot(c)
dev.off()
